Interpolate the weight at agecl output to annual age

### 2020-06-03 InterpolateWeightAtAge.Rmd
testing for 3 species, range of true ages

Plot interpolated results for more NOBA species:

@@

@@

>>>>

Run wrappers and plot interpolated results for multiple NOBA species:

@@

NOBAom <- om_init(here("config/NOBA2config.R"))

# 3 species: 40, 20, 6 age classes
NOBAom_redcodcap <- om_species(c("Redfish", "North_atl_cod", "Capelin"), NOBAom)

rm(NOBAom) #free some memory

@@

Fix bug in omdimensions.R; need to vectorize:

```{r omdimensions-bugfix}

omlist_ss <- NOBAom_redcodcap # multispecies call

n_age_classes <- omlist_ss$funct.group_ss$NumCohorts # works
age_classes <- 1:n_age_classes # nope, only first spp, needed in SS3 writing?

age_classes <- sapply(n_age_classes, seq)
names(age_classes)<-survspp

n_annages <- n_age_classes * omlist_ss$funct.group_ss$NumAgeClassSize # works
annages <- 1:n_annages # nope, only first spp, needed in SS3 writing?

annages <- sapply(n_annages, seq)
names(annages)<-survspp

# dimensioning survey in 3sppsurvey.R
survspp <- omlist_ss$species_ss # works
surveffic <- data.frame(species=survspp,
                     efficiency=rep(1.0,length(survspp)))  # works
survselex <- data.frame(species=rep(survspp, each=n_annages), # nope! 
                        agecl=rep(c(1:n_annages),length(survspp)),
                        selex=rep(1.0,length(survspp)*n_annages))
surveffN <- data.frame(species=survspp, effN=rep(1000, length(survspp))) # works
surv_cv <- data.frame(species=survspp, cv=rep(0.1,length(survspp))) # works

#dimensioned for annual ages rather than age classes
survselex <- data.frame(species=rep(survspp, n_annages), #  
                        agecl=unlist(sapply(n_annages,seq)),
                        selex=rep(1.0,sum(n_annages)))

New config files needed for multispecies pulls:

`3sppsurvey.R` configures the fishery independent survey and looks like this:

```{r, code = readLines("./config/3sppsurvey.R"), eval=F}
```

`3sppfishery.R` configures the fishery dependent data and looks like this:

```{r, code = readLines("./config/3sppfishery.R"), eval=F}
```

Fix multispecies bug in om_index function:
```{r omindex-bugfix}

# original  
wtage <- data.frame(species=rep(survspp, each=max(age_classes)), #nope
                      agecl=rep(c(1:max(age_classes)),length(survspp)), #nope
                      wtAtAge=rep(1000.0,length(survspp)*max(age_classes))) #nope

# age_classes is now a list 1:n_age_classes by species
# this is still dimensioned by agecl not true age
wtage <- data.frame(species=rep(survspp, n_age_classes), 
                      agecl=unlist(sapply(n_age_classes,seq)), 
                      wtAtAge=rep(1000.0,sum(n_age_classes)))

Try index step again:

```{r indcomp-test}

NOBAom_redcodcap_ind <- om_index(usersurvey = here("config/3sppsurvey.R"), 
                           userfishery = here("config/3sppfishery.R"),
                           omlist_ss = NOBAom_redcodcap, 
                           n_reps = 1, 
                           save = TRUE)

om_index works, om_comps runs for survey and produces age, length, weight output, produces fishery age output, but fails calling the age2length function.

check fishery observed age comp:

```{r debugcomps, eval=FALSE}

catch_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
catch_age_comp <- catch_age_comp[[1]]

filter(catch_age_comp, species=="North_atl_cod")
filter(catch_age_comp, species=="Redfish")
filter(catch_age_comp, species=="Capelin")

#snippets from calc_age2length
nums <- filter(catch_age_comp, species=="Capelin")
#calculate mean length at age
mulen <- nums
muweight <- nums

#needed stuff from om_comps
#Get catch weights for length comp calc
  # aggregate true resn per fishery subset design
  catch_aggresnss <- atlantisom::aggregateDensityData(dat = omlist_ss$trueresn_ss,
                                                      time = fishtime,
                                                      species = survspp,
                                                      boxes = fishboxes)

  # aggregate true structn fishery subsetdesign
  catch_aggstructnss <- atlantisom::aggregateDensityData(dat = omlist_ss$truestructn_ss,
                                                         time = fishtime,
                                                         species = survspp,
                                                         boxes = fishboxes)

  #dont sample these, just aggregate them using median
  structn <- atlantisom::sample_fish(catch_aggstructnss, fisheffN, sample = FALSE)

  resn <- atlantisom::sample_fish(catch_aggresnss, fisheffN, sample = FALSE)

  # more snippets from calc_age2length
  # extract rows from structn and resn that match the rows in nums, which are only non-zeroes
resn.ind <- with(resn,paste(species,'.',agecl,'.',polygon,'.',layer,'.',time,sep=""))
num.ind <- with(nums,paste(species,'.',agecl,'.',polygon,'.',layer,'.',time,sep=""))
pick <- match(num.ind,resn.ind)
SRN <- resn$atoutput[pick] + structn$atoutput[pick]

# get weight-length parameters
li_a_use <- biolprm$wl[match(fgs$Code[match(nums$species,fgs$Name)],biolprm$wl[, 1]), 2]
li_b_use <- biolprm$wl[match(fgs$Code[match(nums$species,fgs$Name)],biolprm$wl[, 1]), 3]

#calc mean length and weight at age
mulen$atoutput <- ((biolprm$kgw2d*biolprm$redfieldcn*SRN)/(1000*li_a_use))^(1/li_b_use)
muweight$atoutput <- li_a_use*mulen$atoutput^li_b_use

upper.bins <- 1:maxbin
lower.bins <- c(0,upper.bins[-length(upper.bins)])
lenfreq <- NULL

# well, match does return NA for capelin, and this is what breaks the comparison using 
# the max function (returns NA). adding na.rm=TRUE to line 86
if(maxbin<max(mulen$atoutput)){
  print("Warning: maximum bin size is smaller than the longest fish in the sample. Fish above the maximum bin size will be removed from length compositions.")
}

groups <- unique(as.factor(structn$species)) 
CVlenage = 0.1
# but will NAs break the following?
for (irow in 1:nrow(mulen))
#for (irow in 1:500)
  {
  group <- nums$species[irow]
  igroup <- which(groups==group)
  box <- nums$polygon[irow]
  layer <- nums$layer[irow]
  time <- nums$time[irow]
  age <- nums$agecl[irow]

  sigma = sqrt(log((CVlenage^2)+1))
  muuse <- log(mulen$atoutput[irow]) - 0.5*(sigma^2)
  CumFracperbin <- plnorm(upper.bins,muuse,sigma)
  Fracperbin <- c(CumFracperbin[1],diff(CumFracperbin))
  natlength = Fracperbin*nums$atoutput[irow]
  results <- cbind(mulen[irow,],lower.bins,upper.bins, row.names = NULL) # add row.names = NULL?
  results$atoutput <- round(natlength,0)
  #results <- results[results$atoutput>0,]
  lenfreq <- rbind(lenfreq,results) # add row.names = NULL?
}

remove.zeroes = TRUE
#get rid of zero rows.
if (remove.zeroes) lenfreq <- lenfreq[lenfreq$atoutput>0,]

#output. natlength now has additional columns because of need to store length bin info
lenout <- NULL
lenout$mulen <- mulen
lenout$muweight <- muweight
lenout$natlength <- lenfreq

# ok, works but adds NA for Capelin age classes where no numbers were sampled.
# could crank up sample size or just live with this.

Try om_comps step again:

```{r comps-redo}

NOBAom_redcodcap_comp <- om_comps(usersurvey = here("config/3sppsurvey.R"), 
                           userfishery = here("config/3sppfishery.R"),
                           omlist_ss = NOBAom_redcodcap, 
                           n_reps = 1, 
                           save = TRUE)
```
